RNA-seq from 4 cell populations

### 2021-07-30 deconvolution/fans4/molec_profiling.Rmd
bug fix

df_hugo = select(org.Hs.eg.db, unique(as.character(df$Var1)), "SYMBOL", "ENSEMBL")
df = merge(df, df_hugo, by.x="Var1", by.y="ENSEMBL")
df = df[!is.na(df$SYMBOL),]

@@

  geneTab = select(ensdb, keys=names(isexpr[isexpr]), columns=c("GENEID", "GENEBIOTYPE"), keytype="GENEID")

@@

    geneTab = select(ensdb, keys=rownames(tab), columns=c("GENEID", "GENEBIOTYPE"), keytype="GENEID")

>>>>

df_hugo = AnnotationDbi::select(org.Hs.eg.db, unique(as.character(df$Var1)), "SYMBOL", "ENSEMBL")
df = merge(df, df_hugo, by.x="Var1", by.y="ENSEMBL")
df = df[!is.na(df$SYMBOL),]

@@

  geneTab = AnnotationDbi::select(ensdb, keys=names(isexpr[isexpr]), columns=c("GENEID", "GENEBIOTYPE"), keytype="GENEID")

@@

    geneTab = AnnotationDbi::select(ensdb, keys=rownames(tab), columns=c("GENEID", "GENEBIOTYPE"), keytype="GENEID")
